---
title: "Google Mobility 04-11"
author: "Thomas Li"
date: "4/11/2021"
output: pdf_document
---
```{r}
library(pacman)
p_load(readr,COVID19,leaps,ggplot2,tidyverse,dplyr,car)
```


```{r message=FALSE}
# region mobility report
region_mobility21 <- read_csv("2021_US_Region_Mobility_Report.csv")
region_mobility20 <- read_csv("2020_US_Region_Mobility_Report.csv")
region_mobility20.21 <- merge(x = region_mobility20, y = region_mobility21, all = T)
```

Subsetting Google Mobility data to for linear regression model
```{r}
# subset dataframe range to CA only
ca_mobility20.21 <- region_mobility20.21 %>% 
  filter(sub_region_1 == "California", date >= "2020-03-15", date <= "2021-03-14")

# remove unique identifier columns
ca_mobility.col <- ca_mobility20.21[,-c(5:8)]

# remove NA and convert to positive decimals
ca_mobility.dat <- na.omit(ca_mobility.col) %>%
  mutate(retail_and_recreation_percent_change_from_baseline = retail_and_recreation_percent_change_from_baseline/100+0.9, grocery_and_pharmacy_percent_change_from_baseline = grocery_and_pharmacy_percent_change_from_baseline/100+0.9,
         parks_percent_change_from_baseline = 
           parks_percent_change_from_baseline/100+0.9,
         transit_stations_percent_change_from_baseline =
           transit_stations_percent_change_from_baseline/100+0.9,
         workplaces_percent_change_from_baseline = 
           workplaces_percent_change_from_baseline/100+0.9,
         residential_percent_change_from_baseline = 
           residential_percent_change_from_baseline/100+0.9)
head(ca_mobility.dat)
```


Covid-19 base data
```{r}
# covid19 data
cacovid19data <- covid19("US", level = 2) %>% 
  filter(administrative_area_level_2 == "California", date >= "2020-03-15", date <= "2021-03-14")

base_data <- subset(cacovid19data, select = c("date", "confirmed", "deaths", "tests", "latitude"  , "longitude", "population",  "school_closing", "workplace_closing",  "gatherings_restrictions", "stay_home_restrictions", "internal_movement_restrictions", "information_campaigns", "testing_policy", "contact_tracing", "stringency_index"))
```

Factoring base data
```{r}
# covid19 data factors
fschool_closing = as.factor(base_data$school_closing)
fworkplace_closing <- as.factor(base_data$workplace_closing)
fgatherings_restrictions <- as.factor(base_data$gatherings_restrictions)
fstay_home_restrictions <- as.factor(base_data$stay_home_restrictions)
finternal_movement_restrictions <- as.factor(base_data$internal_movement_restrictions)
finformation_campaigns <- as.factor(base_data$information_campaigns)
ftesting_policy <- as.factor(base_data$testing_policy)
fcontact_tracing <- as.factor(base_data$contact_tracing)
```

Attaching factors to base data
```{r}
# attach factors to base covid19 data
attach(base_data)

fbase_data <- base_data %>% 
  mutate(fschool_closing, fworkplace_closing, fgatherings_restrictions,
         fstay_home_restrictions, finternal_movement_restrictions,
         finformation_campaigns, ftesting_policy, fcontact_tracing)

```

Merging covid 19 base data and google mobility data
```{r}
# merge covid19 and google mobility data
cacovid_mobility <- merge(x = ca_mobility.dat, y = fbase_data, all = T)
head(cacovid_mobility)
tail(cacovid_mobility)
```


We ran an initial fitted linear model of Google mobility and 
Covid 19 data. We removed all constant data as well as singularities. 
Removed data includes: Longitude, Latitude, Population, finternal_movement_restrictions2, finformation_campaigns2
```{r}
# full fitted model
google.full1 <- lm(deaths ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + parks_percent_change_from_baseline + transit_stations_percent_change_from_baseline + workplaces_percent_change_from_baseline + residential_percent_change_from_baseline + date + confirmed + tests + latitude  + longitude + population +  fschool_closing +
            fworkplace_closing + fgatherings_restrictions + fstay_home_restrictions + finternal_movement_restrictions  +
            finformation_campaigns + ftesting_policy + fcontact_tracing + stringency_index, data = cacovid_mobility)

# full fitted model w/o non
google.full <- lm(deaths ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + parks_percent_change_from_baseline + transit_stations_percent_change_from_baseline + workplaces_percent_change_from_baseline + residential_percent_change_from_baseline + date + confirmed + tests + fschool_closing +
            fworkplace_closing + fgatherings_restrictions + fstay_home_restrictions + ftesting_policy + fcontact_tracing + stringency_index, data = cacovid_mobility)
summary(google.full1)
summary(google.full)

plot(google.full, which = c(1,2))
```


```{r}
# null model
google.red <- lm(deaths ~ 1, data = cacovid_mobility)
```

AIC selected model:13 predictors
-retail_and_recreation_percent_change_from_baseline
-grocery_and_pharmacy_percent_change_from_baseline
-transit_stations_percent_change_from_baseline
-residential_percent_change_from_baseline
-confirmed
-fschool_closing
-fworkplace_closing
-fgatherings_restrictions
-fstay_home_restrictions 
-finternal_movement_restrictions
-ftesting_policy
-fcontact_tracing  
-stringency_index

    
```{r}
# variable selection with AIC
step(google.full, scope = list(lower = google.red, upper = google.full), trace = 0)

var_selectAIC <- lm(deaths ~ retail_and_recreation_percent_change_from_baseline  
+grocery_and_pharmacy_percent_change_from_baseline 
+transit_stations_percent_change_from_baseline  
+residential_percent_change_from_baseline 
+confirmed 
+fschool_closing  
+fworkplace_closing 
+fgatherings_restrictions 
+fstay_home_restrictions 
+finternal_movement_restrictions 
+ftesting_policy 
+fcontact_tracing
+stringency_index, data = cacovid_mobility)

summary(var_selectAIC)

plot(var_selectAIC, which = c(1,2))
```


BIC selected model:12 predictors
-retail_and_recreation_percent_change_from_baseline  
-grocery_and_pharmacy_percent_change_from_baseline 
-transit_stations_percent_change_from_baseline  
-residential_percent_change_from_baseline 
-confirmed 
-fschool_closing  
-fworkplace_closing 
-fgatherings_restrictions 
-fstay_home_restrictions 
-finternal_movement_restrictions 
-ftesting_policy 
-fcontact_tracing

```{r}
# variable selection with BIC
n <- length(cacovid_mobility$deaths)
step(google.full, scope = list(lower = google.red, upper = google.full), trace = 0, k = log(n))

var_selectBIC <- lm(deaths ~ retail_and_recreation_percent_change_from_baseline  
+grocery_and_pharmacy_percent_change_from_baseline 
+transit_stations_percent_change_from_baseline  
+residential_percent_change_from_baseline 
+confirmed 
+fschool_closing  
+fworkplace_closing 
+fgatherings_restrictions 
+fstay_home_restrictions 
+finternal_movement_restrictions 
+ftesting_policy 
+fcontact_tracing, data = cacovid_mobility)

summary(var_selectBIC)
```
```{r}
# diagnostic plots for BIC selection
plot(var_selectBIC, which = c(1,2))
```


```{r}
# best subset regression
subset.summary <- summary(regsubsets(deaths ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + parks_percent_change_from_baseline + transit_stations_percent_change_from_baseline + workplaces_percent_change_from_baseline + residential_percent_change_from_baseline + date + confirmed + tests + fschool_closing +
            fworkplace_closing + fgatherings_restrictions + fstay_home_restrictions + ftesting_policy + fcontact_tracing + stringency_index, data = cacovid_mobility))

subset.summary
subset.summary$adjr2
subset.summary$cp
subset.summary$bic
```

After model selection for lowest cp and BIC, and highest adjusted R-squared
```{r}
# after model selection (7 predictors)
regsubset.fit <- lm(deaths ~ date + tests + fschool_closing + fworkplace_closing + fstay_home_restrictions + ftesting_policy +fcontact_tracing, data = cacovid_mobility)

summary(regsubset.fit)
```

Relationships between variables in the preferred model
```{r}
cacovid_pairs <- cacovid_mobility %>% 
  select(deaths, date, tests, fschool_closing, fworkplace_closing, 
    fstay_home_restrictions, ftesting_policy, fcontact_tracing) 
pairs(cacovid_pairs)
```


Running a residuals vs. fitted and Q-Q plot show that the initial model does not follow a normal distribution. 
```{r}
# diagnostic plots for regsubset
plot(regsubset.fit, which = c(1,2))
```
Transformation of all non-factor predictors. The confirmed 
response can either use a log transformation or a square root transformation. 
```{r}
pt <- powerTransform(cbind(cacovid_mobility$tests) ~ 1)
summary(pt)
```

Either no transformation or square root transformation for the response
```{r}
# optimal lambda for response from full model
boxCox(regsubset.fit)
```

After checking diagnostic plots for all transformation suggestions, we see that a
the square root transformation closest meets assumptions for linear regression.
```{r}
# square root transformation for both deaths and tests
regsubset.trans1 <- lm(sqrt(deaths) ~ date + sqrt(tests) + fschool_closing + fworkplace_closing + fstay_home_restrictions + ftesting_policy +fcontact_tracing, data = cacovid_mobility)

# square root transformation for tests
regsubset.trans2 <- lm(deaths ~ date + sqrt(tests) + fschool_closing + fworkplace_closing + fstay_home_restrictions + ftesting_policy +fcontact_tracing, data = cacovid_mobility)

# square root transformation for deaths and log transformation for tests
regsubset.trans3 <- lm(sqrt(deaths) ~ date + log(tests) + fschool_closing + fworkplace_closing + fstay_home_restrictions + ftesting_policy +fcontact_tracing, data = cacovid_mobility)

# log transformation for tests
regsubset.trans4 <- lm(deaths ~ date + log(tests) + fschool_closing + fworkplace_closing + fstay_home_restrictions + ftesting_policy +fcontact_tracing, data = cacovid_mobility)

# transformed model with only numerical variables
regsubset.trans5 <- lm(sqrt(deaths) ~ date + sqrt(tests))
plot(regsubset.trans5, which = c(1,2))

# transformed model with only categorical variables
regsubset.trans6 <- lm(sqrt(deaths) ~ fschool_closing + fworkplace_closing + fstay_home_restrictions + ftesting_policy +fcontact_tracing, data = cacovid_mobility)
plot(regsubset.trans6, which = c(1,2))

regsubset.trans7 <- lm(sqrt(deaths) ~ date + I(tests^(1/3)) + fschool_closing + fworkplace_closing + fstay_home_restrictions + ftesting_policy +fcontact_tracing, data = cacovid_mobility)

# linear fit with google mobility and only categorical values from base covid
google.factors <- lm(deaths ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + parks_percent_change_from_baseline + transit_stations_percent_change_from_baseline + workplaces_percent_change_from_baseline + residential_percent_change_from_baseline + fschool_closing + fworkplace_closing + fstay_home_restrictions + ftesting_policy +fcontact_tracing, data = cacovid_mobility)

plot(google.factors, which = c(1,2))

boxCox(google.factors)

google.factors1 <- lm(sqrt(deaths) ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + parks_percent_change_from_baseline + transit_stations_percent_change_from_baseline + workplaces_percent_change_from_baseline + residential_percent_change_from_baseline, data = cacovid_mobility)

plot(google.factors1, which = c(1,2))

boxCox(google.factors1)

plot(regsubset.trans1, which = c(1,2))
plot(regsubset.trans2, which = c(1,2))
plot(regsubset.trans3, which = c(1,2))
plot(regsubset.trans4, which = c(1,2))
```


```{r}
# full google model (summary and diagnostics) - workplaces not sig
google.dat <- lm(deaths ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + parks_percent_change_from_baseline + transit_stations_percent_change_from_baseline + workplaces_percent_change_from_baseline + residential_percent_change_from_baseline, data = cacovid_mobility)

summary(google.dat)

plot(google.dat)

# variable selection (5 var model) - suggests to take out workplaces
google.varselect <- summary(regsubsets(deaths ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + parks_percent_change_from_baseline + transit_stations_percent_change_from_baseline + workplaces_percent_change_from_baseline + residential_percent_change_from_baseline, data = cacovid_mobility))

google.varselect
google.varselect$adjr2
google.varselect$cp
google.varselect$bic

# linear model fit without workplace variable
google.fivevar <- lm(deaths ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + parks_percent_change_from_baseline + transit_stations_percent_change_from_baseline + residential_percent_change_from_baseline, data = cacovid_mobility)

summary(google.fivevar)

plot(google.fivevar)
```

```{r}
# transformation of predictors w/o workplace
pt1 <- powerTransform(cbind(cacovid_mobility$retail_and_recreation_percent_change_from_baseline, cacovid_mobility$grocery_and_pharmacy_percent_change_from_baseline, cacovid_mobility$parks_percent_change_from_baseline, cacovid_mobility$transit_stations_percent_change_from_baseline, cacovid_mobility$residential_percent_change_from_baseline) ~ 1)

summary(pt1)

# transformation of predictors w/ workplace
pt2 <- powerTransform(cbind(cacovid_mobility$retail_and_recreation_percent_change_from_baseline, cacovid_mobility$grocery_and_pharmacy_percent_change_from_baseline, cacovid_mobility$parks_percent_change_from_baseline, cacovid_mobility$transit_stations_percent_change_from_baseline, cacovid_mobility$workplaces_percent_change_from_baseline, cacovid_mobility$residential_percent_change_from_baseline) ~ 1)

summary(pt2)

# 5 var model fit with transformed predictors
google.vartrans <- lm(deaths ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + I(parks_percent_change_from_baseline^1/3) + log(transit_stations_percent_change_from_baseline) + I(residential_percent_change_from_baseline^-3), data = cacovid_mobility)

par(mfrow = c(1,2))
plot(google.vartrans, which = c(1,2))
summary(google.vartrans)

# 6 var model fit with transformed predictors
google.vartrans6 <- lm(deaths ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + I(parks_percent_change_from_baseline^1/3) + log(transit_stations_percent_change_from_baseline) + workplaces_percent_change_from_baseline + I(residential_percent_change_from_baseline^-2), data = cacovid_mobility)

par(mfrow = c(1,2))
plot(google.vartrans6, which = c(1,2))
summary(google.vartrans6)
```

```{r}

# transformation of response 5 var
boxCox(google.vartrans)

# transformation of response 6 var
boxCox(google.vartrans6)

# linear fit with full transformation (suggested model via variable selection)
google.fulltrans <- lm(sqrt(deaths) ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + I(parks_percent_change_from_baseline^1/3) + log(transit_stations_percent_change_from_baseline) + I(residential_percent_change_from_baseline^-3), data = cacovid_mobility)

# linear fit with full transformation and ignoring variable selection workplace^-2
google.workplace2 <- lm(sqrt(deaths) ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + I(parks_percent_change_from_baseline^1/3) + log(transit_stations_percent_change_from_baseline) + workplaces_percent_change_from_baseline + I(residential_percent_change_from_baseline^-2), data = cacovid_mobility)

# linear fit with full transformation and ignoring variable selection workplace^-3
google.workplace3 <- lm(sqrt(deaths) ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + I(parks_percent_change_from_baseline^1/3) + log(transit_stations_percent_change_from_baseline) + workplaces_percent_change_from_baseline + I(residential_percent_change_from_baseline^-3), data = cacovid_mobility)

# comparison of final models with and without workplace var 
summary(google.workplace2)
summary(google.workplace3)
par(mfrow = c(1,2))
plot(google.workplace2, which = c(1,2))
plot(google.workplace3, which = c(1,2))

summary(google.fulltrans)
par(mfrow = c(1,2))
plot(google.fulltrans, which = c(1,2))
plot(google.workplace2, which = c(1,2))

# outliers and leverage points plot (only two bad leverage points, but do not significantly affect the model by removing them)
plot(hatvalues(google.workplace), rstandard(google.workplace), xlab = "Leverage", 
     ylab = "Standardized Residuals", lwd = 0.1, cex = 0.8, ylim = c(-6,6), xlim = c(0,0.01))
abline(v = 4*(p+1)/n, col = "red", lty = 2)
abline(h = c(-4,4), col = "blue", lty =2)

# leverage points
p <- 7
n <- nrow(cacovid_mobility)
google_hat <- hatvalues(google.workplace)
which(google_hat > 4*(p+1)/n)

# outliers
google.std <- rstandard(google.workplace)
which(abs(google.std) > 4)

# conclusion is that the 6 model variable, after transformations, has a slightly higher adjusted R-squared and workplace is significant
# also QQ plot and residuals looks slightly better with 6 model variable
summary(google.workplace)
```

```{r}
# linear fit with full transformation and adding back in categorical data
google.workplace3 <- lm(sqrt(deaths) ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + I(parks_percent_change_from_baseline^1/3) + log(transit_stations_percent_change_from_baseline) + workplaces_percent_change_from_baseline + I(residential_percent_change_from_baseline^-2) + fschool_closing + fworkplace_closing + fstay_home_restrictions + ftesting_policy + fcontact_tracing, data = cacovid_mobility)
summary(google.workplace3)
plot(google.workplace3, which = c(1,2))
```


```{r}
summary(regsubset.trans1)
```

Checking for high leverage points
```{r}
# leverage point calculations
p <- 7
n <- nrow(cacovid_mobility)
cacovid_hat <- hatvalues(regsubset.trans1)
which(cacovid_hat > 4*(p+1)/n)
```

Checking for outliers, set $|r_i|>2$ 
Note: setting $|r_i|$ to 3 means there are no outliers
```{r}
# outlier calculations
cacovid_std <- rstandard(regsubset.trans1)
which(abs(cacovid_std) > 2)
```

Plot to look for bad leverage points
```{r}
# plot of high leverage points and outliers
plot(hatvalues(regsubset.trans1), rstandard(regsubset.trans1), xlab = "Leverage", 
     ylab = "Standardized Residuals", lwd = 0.1, cex = 0.8)
abline(v = 4*(p+1)/n, col = "red", lty = 2)
abline(h = c(-2,2), col = "blue", lty =2)
```
There are no Cook's points that are greater than 0.5
No points will be removed 
```{r}
# Cook's points and hat values
cacovid.cooks <- cooks.distance(regsubset.trans1)
which(cacovid.cooks > 4/(n-p-1))
influenceIndexPlot(regsubset.trans1, vars = "Cook")
influenceIndexPlot(regsubset.trans1, vars = "hat")
```
Alternative: We remove data points with high Cook's values relative to other points.
This does not affect the significance of the transformed model regsubset.trans1
Ultimately, we will not remove high Cook's points
```{r}
cacovid_mobility1 <- cacovid_mobility[-c(12484:12596),]

regsubset.cooks <- lm(sqrt(deaths) ~ date + sqrt(tests) + fschool_closing + fworkplace_closing + fstay_home_restrictions + ftesting_policy +fcontact_tracing, data = cacovid_mobility1) 
summary(regsubset.cooks)
```

```{r}
plot(regsubset.cooks)
```

```{r}
influenceIndexPlot(regsubset.cooks, vars = "Cook")
```

Proposed Model of variable selection with Google mobility and categorical data. 
All Google mobility data was taken out.

Response: square root of deaths

Predictors:
-square root of tests
-fschool_closing
-fworkplace_closing
-fstay_home_restrictions
-ftesting_policy
-fcontact_tracing
```{r}
regsubset.trans1 <- lm(sqrt(deaths) ~ date + sqrt(tests) + fschool_closing + 
                         fworkplace_closing + fstay_home_restrictions + ftesting_policy +fcontact_tracing, data = cacovid_mobility)
```


## Google Mobility Write-up
Our initial objective was to find out if running a linear regression of the 
Google Mobility data with the Covid-19 data had any significance in predicting 
the rate of deaths due to Covid-19. The Google mobility data recorded 
travel trends to categorized locations during the Covid-19 pandemic. This data 
is compared against a baseline reading; that is, the median value of each day of 
the week during a 5‑week period (Jan 3 – Feb 6, 2020).

In order to choose the ideal model, we fit the combined data and ran variable 
selections to identify the model with the lowest cp and BIC values, and the
highest adjusted R-squared value. The result of this selection process concluded
that the travel trends of the Google mobility data are not significant in 
predicting deaths due to Covid-19. That is, the final model selected only 
includes data from the Covid-19 data set.


```{r}
# final model comparison without transformations
bd <- lm(deaths ~ date + confirmed + tests + fschool_closing +
            fworkplace_closing + fgatherings_restrictions + fstay_home_restrictions   +
            ftesting_policy + fcontact_tracing + stringency_index, data = cacovid_mobility)

gm <- lm(deaths ~ date + tests + fschool_closing + fworkplace_closing + fstay_home_restrictions + ftesting_policy +fcontact_tracing, data = cacovid_mobility)

anova(gm, bd)
```


```{r}
google.workplace4 <- lm(deaths ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + parks_percent_change_from_baseline + transit_stations_percent_change_from_baseline + workplaces_percent_change_from_baseline + residential_percent_change_from_baseline + fschool_closing + fworkplace_closing + fstay_home_restrictions + ftesting_policy +fcontact_tracing, data = cacovid_mobility)

# linear fit with full transformation and adding back in all categorical data
google.workplace3 <- lm(sqrt(deaths) ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + I(parks_percent_change_from_baseline^1/3) + log(transit_stations_percent_change_from_baseline) + workplaces_percent_change_from_baseline + I(residential_percent_change_from_baseline^-2) + fschool_closing + fworkplace_closing + fstay_home_restrictions + ftesting_policy +fcontact_tracing, data = cacovid_mobility)
summary(google.workplace3)
plot(google.workplace3, which = c(1,2))
```


~~~~~~~~~~~~~~ UPDATE MAY 10, 2021 ~~~~~~~~~~~~~~ 

Linear fit with Google mobility and categorical base Covid data

```{r}
google.category <- lm(deaths ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + parks_percent_change_from_baseline + transit_stations_percent_change_from_baseline + workplaces_percent_change_from_baseline + residential_percent_change_from_baseline + fschool_closing + fworkplace_closing + fstay_home_restrictions + ftesting_policy +fcontact_tracing, data = cacovid_mobility)

summary(google.category)
plot(google.category, which = c(1,2))
```

Variable selection using regsubset(). 

```{r}
google.subset <- summary(regsubsets(deaths ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + parks_percent_change_from_baseline + transit_stations_percent_change_from_baseline + workplaces_percent_change_from_baseline + residential_percent_change_from_baseline + fschool_closing + fworkplace_closing + fstay_home_restrictions + ftesting_policy +fcontact_tracing, data = cacovid_mobility))

google.subset
google.subset$adjr2
google.subset$cp
google.subset$bic
```

Six predictor model chosen

```{r}
google.category1 <- lm(deaths ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + fschool_closing + fworkplace_closing +  ftesting_policy +fcontact_tracing, data = cacovid_mobility)

summary(google.category1)

plot(google.category1, which = c(1,2))
```

retail_and_recreation_percent_change_from_baseline needs a transformation to the power of 3/2
grocery_and_pharmacy_percent_change_from_baseline needs a transformation to the power of 3/4

```{r}
google.transform1 <- powerTransform(cbind(cacovid_mobility$retail_and_recreation_percent_change_from_baseline, 
                                          cacovid_mobility$grocery_and_pharmacy_percent_change_from_baseline) ~ 1)

summary(google.transform1)
```

After using powerTransform(), we decided on transforming retail and recreation 
to the power of 3/2 and transforming grocery and pharmacy to the power of 3/4

```{r}
google.category2 <- lm(deaths ~ I(retail_and_recreation_percent_change_from_baseline^(3/2)) + I(grocery_and_pharmacy_percent_change_from_baseline^(3/4)) + fschool_closing + fworkplace_closing +  ftesting_policy + fcontact_tracing, data = cacovid_mobility)

summary(google.category2)
plot(google.category2, which = c(1,2))
```

boxCox() suggests a square root transformation for the response

```{r}
bc.transform <- boxCox(google.category2, lambda=seq(-1, 1, by=0.1))
bc.transform$x[which.max(bc.transform$y)]
```

This is the fully transformed linear model

```{r}
google.category3 <- lm(sqrt(deaths) ~ I(retail_and_recreation_percent_change_from_baseline^(3/2)) + I(grocery_and_pharmacy_percent_change_from_baseline^(3/4)) + fschool_closing + fworkplace_closing +  ftesting_policy + fcontact_tracing, data = cacovid_mobility)

summary(google.category3)
plot(google.category3, which = c(1,2))
```

We plot the leverage points and outliers to check for bad leverage points.

```{r}
# plot of high leverage points and outliers
plot(hatvalues(google.category3), rstandard(google.category3), xlab = "Leverage", 
     ylab = "Standardized Residuals", lwd = 0.8, cex = 0.8, ylim = c(-4,4))
abline(v = 4*(p+1)/n, col = "red", lty = 2)
abline(h = c(-3,3), col = "blue", lty =2)
```

Checking for high leverage points and outliers. There are no bad leverage points.

```{r}
# leverage point calculations
p <- 6
n <- nrow(cacovid_mobility)
google.hat <- hatvalues(google.category3)
which(google.hat > 3*mean(google.hat))

# outlier calculations
google.std <- rstandard(google.category3)
which(abs(google.std) > 3)
```

Visually checking Cook's and hat values. It does not look like it is necessary to remove any point.

```{r}
# Cook's points and hat values
google.cooks <- cooks.distance(google.category3)
which(google.cooks > 4/(n-p-1))
influenceIndexPlot(google.category3, vars = "Cook")
influenceIndexPlot(google.category3, vars = "hat")
```

We remove the highest Cook's value and see that there is no significant difference between the
two models after comparing the diagnostic plots and summaries.

```{r}
cacovid_mobility65 <- cacovid_mobility[-65, ]

google.category4 <- lm(sqrt(deaths) ~ I(retail_and_recreation_percent_change_from_baseline^(3/2)) + I(grocery_and_pharmacy_percent_change_from_baseline^(3/4)) + fschool_closing + fworkplace_closing +  ftesting_policy + fcontact_tracing, data = cacovid_mobility65)

summary(google.category4)
plot(google.category4, which = c(1,2))

google.cooks1 <- cooks.distance(google.category4)
which(google.cooks1 > 4/(n-p-1))
influenceIndexPlot(google.category4, vars = "Cook")
```

