---
title: "Google Mobility 04-11"
author: "Thomas Li"
date: "4/11/2021"
output: pdf_document
---
```{r}
library(pacman)
p_load(readr,COVID19,leaps,ggplot2,tidyverse,dplyr,car)
```


```{r message=FALSE}
# region mobility report
region_mobility21 <- read_csv("2021_US_Region_Mobility_Report.csv")
region_mobility20 <- read_csv("2020_US_Region_Mobility_Report.csv")
region_mobility20.21 <- merge(x = region_mobility20, y = region_mobility21, all = T)
```

Subsetting Google Mobility data to for linear regression model
```{r}
# subset dataframe range to CA only
ca_mobility20.21 <- region_mobility20.21 %>% 
  filter(sub_region_1 == "California", date >= "2020-03-15", date <= "2021-03-15")

# remove unique identifier columns
ca_mobility.col <- ca_mobility20.21[,-c(5:8)]

# remove N/A
ca_mobility.omit <- na.omit(ca_mobility.col)

# convert percentages to decimals and make all values positive 
ca_mobility.dat <- (ca_mobility.omit[,6:11]/100)+0.9
View(ca_mobility.dat)
```


```{r}

# covid19 data
base_data <- subset(cacovid19data, select = c("date", "confirmed", "deaths", "administrative_area_level_2", "latitude"  , "longitude", "population",  "school_closing", "workplace_closing", "gatherings_restrictions", "stay_home_restrictions", "internal_movement_restrictions", "information_campaigns", "testing_policy", "contact_tracing", "stringency_index"))
```


```{r}
# covid19 data factors
fschool_closing = as.factor(base_data$school_closing)
fworkplace_closing <- as.factor(base_data$workplace_closing)
fgatherings_restrictions <- as.factor(base_data$gatherings_restrictions)
fstay_home_restrictions <- as.factor(base_data$stay_home_restrictions)
finternal_movement_restrictions <- as.factor(base_data$internal_movement_restrictions)
finformation_campaigns <- as.factor(base_data$information_campaigns)
ftesting_policy <- as.factor(base_data$testing_policy)
fcontact_tracing <- as.factor(base_data$contact_tracing)
```


```{r}
# attach factors to base covid19 data
attach(base_data)

fbase_data <- base_data %>% 
  mutate(fschool_closing, fworkplace_closing, fgatherings_restrictions,
         fstay_home_restrictions, finternal_movement_restrictions,
         finformation_campaigns, ftesting_policy, fcontact_tracing)

```



```{r}
# merge covid19 and google mobility data
cacovid_mobility <- merge(x = ca_mobility.dat, y = fbase_data, all = T)
head(cacovid_mobility)
```

We ran an initial fitted linear model with all nonconstant Google mobility and Covid 19
data. Immediately, we see that all six predictors from the Google mobility data set 
do not have significance.

```{r}
# full fitted model (omitted lat, long, popln because it stays constant)
google.full <- lm(deaths ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + parks_percent_change_from_baseline + transit_stations_percent_change_from_baseline + workplaces_percent_change_from_baseline + residential_percent_change_from_baseline + confirmed +  fschool_closing + fworkplace_closing + fgatherings_restrictions + fstay_home_restrictions + finternal_movement_restrictions  + finformation_campaigns + ftesting_policy + fcontact_tracing + stringency_index, data = cacovid_mobility)

summary(google.full)
```

Running a residuals vs. fitted and Q-Q plot show that the initial model does not 
follow a normal distribution. 
```{r}
# diagnostic plots
plot(google.full, which = c(1,2))
```
Transformation of all non-factor and significant predictors. The confirmed 
response can either use a log transformation or no transformation. The stringency
index should be transformed with a negative squareroot
```{r}
pt <- powerTransform(cbind(cacovid_mobility$confirmed, cacovid_mobility$stringency_index) ~ 1)
summary(pt)
```

No transfomration is necessary
```{r}
# optimal lambda for response from full model
boxCox(google.full)
```


```{r}
# null model
google.red <- lm(deaths ~ 1, data = cacovid_mobility)
boxCox(google.full)
plot(google.log)
```


```{r}
step(google.full, scope = list(lower = google.red, upper = google.full))
```


```{r}
# subset models
subset.summary <- summary(regsubsets(deaths ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + parks_percent_change_from_baseline + transit_stations_percent_change_from_baseline + workplaces_percent_change_from_baseline + residential_percent_change_from_baseline + confirmed +  fschool_closing + fworkplace_closing + fgatherings_restrictions + fstay_home_restrictions + finternal_movement_restrictions  + finformation_campaigns + ftesting_policy + fcontact_tracing + stringency_index, data = cacovid_mobility))

subset.summary
```

```{r}
# after model selection (10 predictors)
regsubset.fit <- lm(deaths ~ confirmed + fschool_closing + fworkplace_closing + fgatherings_restrictions + fstay_home_restrictions + finternal_movement_restrictions + finformation_campaigns + ftesting_policy + fcontact_tracing + stringency_index, data = cacovid_mobility)

summary(regsubset.fit)
```

```{r}
# subset without Google mobility
summary(regsubsets(deaths ~ confirmed + fschool_closing + fworkplace_closing + fgatherings_restrictions + fstay_home_restrictions + finternal_movement_restrictions + finformation_campaigns + ftesting_policy + fcontact_tracing + stringency_index, data = cacovid_mobility))

```

```{r}
step(regsubset.fit, scope = list(lower = google.red, upper = regsubset.fit))
```



```{r}
# All possible models
predict_one <- lm(confirmed ~ retail_and_recreation_percent_change_from_baseline, data = cacovid_mobility)

predict_two <- lm(confirmed ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline, data = cacovid_mobility)

predict_three <- lm(confirmed ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + parks_percent_change_from_baseline, data = cacovid_mobility)

predict_four <- lm(confirmed ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + parks_percent_change_from_baseline + transit_stations_percent_change_from_baseline, data = cacovid_mobility)

predict_five <- lm(confirmed ~ retail_and_recreation_percent_change_from_baseline + grocery_and_pharmacy_percent_change_from_baseline + parks_percent_change_from_baseline + transit_stations_percent_change_from_baseline + workplaces_percent_change_from_baseline, data = cacovid_mobility)

summary(predict_one)
summary(predict_two)
summary(predict_three)
summary(predict_four)
summary(predict_five)

AIC(predict_one)
AIC(predict_two)
AIC(predict_three)
AIC(predict_four)
AIC(predict_five)
AIC(google.full)

BIC(predict_one)
BIC(predict_two)
BIC(predict_three)
BIC(predict_four)
BIC(predict_five)
BIC(google.full)
BIC(google.full)

summary(predict_one)$adj.r.squared
summary(predict_two)$adj.r.squared
summary(predict_three)$adj.r.squared
summary(predict_four)$adj.r.squared
summary(predict_five)$adj.r.squared
summary(google.full)$adj.r.squared
summary(google.log)$adj.r.squared
```


```{r}
summary(google.full)
plot(google.full)
```


```{r}
# powerTransform and invTranPlot only work for positive values
# Yeo-Johnson boxCox works with negative values
summary(powerTransform(cbind(retail_and_recreation_percent_change_from_baseline + 
    grocery_and_pharmacy_percent_change_from_baseline + parks_percent_change_from_baseline + 
    transit_stations_percent_change_from_baseline + workplaces_percent_change_from_baseline + 
    residential_percent_change_from_baseline) ~ 1, merge.dat))
invTranPlot(merge.dat$confirmed ~ merge.dat$retail_and_recreation_percent_change_from_baseline, optimal = T)
```


```{r}
# datahub provided merge
gmr <- "https://www.gstatic.com/covid19/mobility/Global_Mobility_Report.csv"
x   <- covid19(gmr = gmr)
```

