---
title: "STAT 632 Final Project Base Data Exploritory Analysis"
author: "Nic James"
date: "04/15/2020"
output:
  pdf_document: default
  word_document: default
  html_document: default
  html_notebook: default
---

# Project work

Running some preliminary analysis of the COVID-19 Data Hub data.

```{r}
library(pacman)
p_load(COVID19, tidyverse, ggplot2, dplyr)
```

# Using the help function
```{r}
help("covid19")
```

# Create df:

US Data by State
```{r}
uscovid19data <- covid19("US", level = 3)
tail(uscovid19data)
```
What are the names of all of the columns?
```{r}
names(uscovid19data)
```

## Create a new data frame

### What columns do I want for version 1?

* "id"                                 
* "date"                               
* "tests"                              
* "confirmed"                          
* "recovered"                          
* "deaths"                             
* "hosp"                               
* "vent"                               
* "icu"                                
* "administrative_area_level"
* "administrative_area_level_1"
* "administrative_area_level_2"
* "administrative_area_level_3"
* "latitude"  
* "longitude"

#### Not sure I need

* "population" ?
* "iso_alpha_3" ? 
* "iso_alpha_2" ? 
* "iso_numeric" ? 

*Note:* Version 2 will include economic data.

### What am I going to need to add for version 3?

* "vaccines" 
* "school_closing"                     
* "workplace_closing"                  
* "cancel_events"                      
* "gatherings_restrictions"            
* "transport_closing"                  
* "stay_home_restrictions"             
* "internal_movement_restrictions"     
* "international_movement_restrictions"
* "information_campaigns"              
* "testing_policy"                     
* "contact_tracing"                    
* "stringency_index"


I don't have data for tests, recovered, hosp, and icu

```{r}
c_spread <- subset(uscovid19data, select = c("id", "date", "administrative_area_level_2", "administrative_area_level_3","tests", "confirmed", "recovered", "deaths", "hosp", "vent", "icu"))

head(c_spread)
nrow(c_spread)
```

```{r}
summary.data.frame(c_spread)
```